\Large \bf \projtitle

### 2015-05-08 doc/paper/paper.tex
Reword

Typical means for dealing with this situation involve utilizing Content Delivery
Networks (CDNs), but these are usually out of the budgetary constraints for
websites which only experience such loads on an occasional basis. An ideal
solution would be a lightweight means to mimic the benefits of an ordinary
CDN, which is typically backed by a robust network of machines. \\

>>>>

Typical means for dealing with this situation involve utilizing Content
Delivery Networks (CDNs), but these are expensive, especially for websites
which only experience such high loads on an occasional basis. An ideal solution
would be a lightweight means to mimic the benefits of an ordinary CDN, which is
typically backed by a robust network of machines. \\
